---
title: "Ratio Analysis for `r paste0(tools::toTitleCase(gsub('-', ' ', sub('^[0-9]+-', '', sub('\\.xlsx$', '', basename(params$input_file))))), ', ', basename(dirname(params$input_file)))`"
subtitle: "Prepared `r format(Sys.Date(), '%B %d, %Y')`"
format:
  pdf:
    documentclass: article
    geometry: margin=1in
    fontsize: 11pt
    include-in-header: preamble.tex
params:
  input_file: ""
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(DBI)
library(noctua)
library(openxlsx)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggspatial)
library(sf)
library(scales)
library(ccao)
library(assessr)
library(readr)
library(knitr)
library(glue)
library(rosm)
library(grid)

set_default_cachedir("rosm.cache")

input_file <- params$input_file
file_base <- sub("\\.xlsx$", "", basename(input_file))
town_code <- substr(file_base, 1, 2)
year_val <- basename(dirname(input_file))

town_name <- ccao::town_dict %>%
  filter(township_code == town_code) %>%
  pull(township_name) %>%
  first()


# Read desk review inputs

dr_wb <- loadWorkbook(input_file)
dr_vals <- read.xlsx(dr_wb, sheet = 1) %>%
  tibble(.name_repair = "unique") %>%
  select(pin = PIN, desk_review_FMV = Desk.Review.Value)

# Athena: pull model values and the residential PIN universe

noctua_options(unload = TRUE)
conn <- dbConnect(noctua::athena(), rstudio_conn_tab = FALSE)

dr_towns <- town_code

model_vals <- dbGetQuery(
  conn = conn,
  glue_sql(
    read_file("ratio-analysis.sql"),
    .con = conn
  )
)

dbDisconnect(conn)

# Join and compute ratios / price deciles
all_parcels <- dr_vals %>%
  inner_join(select(model_vals, pin), by = "pin") %>%
  full_join(model_vals, by = "pin") %>%
  rename(model_FMV = model_value) %>%
  filter(township_name == town_name) %>%
  mutate(
    sale_date = as.Date(sale_date),
    sale_excluded = if_else(is.na(sale_price), NA, is.na(desk_review_FMV)),
    price_decile = ntile(
      if_else(sale_excluded %in% TRUE, NA_real_, sale_price), 10
    ),
    model_sale_ratio = model_FMV / sale_price,
    desk_review_sale_ratio = desk_review_FMV / sale_price
  )

# Compute statistics
sales_df <- all_parcels %>%
  filter(!is.na(sale_price), !sale_excluded %in% TRUE)

ts <- tibble(
  model_ratio = median(sales_df$model_sale_ratio, na.rm = TRUE),
  model_cod = assessr::cod(sales_df$model_sale_ratio),
  model_prd = assessr::prd(sales_df$model_FMV, sales_df$sale_price),
  model_prb = assessr::prb(sales_df$model_FMV, sales_df$sale_price),
  model_mki = assessr::mki(sales_df$model_FMV, sales_df$sale_price),
  desk_review_ratio = median(sales_df$desk_review_sale_ratio, na.rm = TRUE),
  desk_review_cod = assessr::cod(sales_df$desk_review_sale_ratio),
  desk_review_prd = assessr::prd(
    sales_df$desk_review_FMV, sales_df$sale_price
  ),
  desk_review_prb = assessr::prb(
    sales_df$desk_review_FMV, sales_df$sale_price
  ),
  desk_review_mki = assessr::mki(
    sales_df$desk_review_FMV, sales_df$sale_price
  ),
  price_range = paste(
    scales::dollar(min(sales_df$sale_price)),
    scales::dollar(max(sales_df$sale_price)),
    sep = "–"
  ),
  number_of_sales = nrow(sales_df)
)

decile_stats <- sales_df %>%
  summarize(
    model_ratio = median(model_sale_ratio, na.rm = TRUE),
    model_cod = assessr::cod(model_sale_ratio),
    desk_review_ratio = median(desk_review_sale_ratio, na.rm = TRUE),
    desk_review_cod = assessr::cod(desk_review_sale_ratio),
    price_range = paste(
      scales::dollar(min(sale_price)),
      scales::dollar(max(sale_price)),
      sep = "–"
    ),
    number_of_sales = n(),
    .by = price_decile
  ) %>%
  arrange(price_decile)

# Methods summary values
n_original_sales <- sum(!is.na(all_parcels$sale_price))
n_final_sales <- nrow(sales_df)
n_excluded_sales <- n_original_sales - n_final_sales
n_total_pins <- nrow(all_parcels)
pct_with_sale <- round(n_final_sales / n_total_pins * 100, 1)

sale_dates <- all_parcels$sale_date[!is.na(all_parcels$sale_date)]
min_sale_date <- format(min(sale_dates), "%B %d, %Y")
max_sale_date <- format(max(sale_dates), "%B %d, %Y")


# Metric definitions: name, digits, IAAO lo/hi bounds, band mid and half-span
metric_meta <- tibble(
  name = c("Median Ratio", "COD", "PRD", "PRB", "MKI"),
  digits = c(3, 1, 4, 4, 4),
  lo = c(0.90, 5.0, 0.98, -0.05, 0.90),
  hi = c(1.10, 15.0, 1.03, 0.05, 1.10),
  mid = c(1.000, 10.0, 1.005, 0.00, 1.000),
  half_span = c(0.100, 5.0, 0.025, 0.05, 0.100),
  standard_label = c(
    "0.90 -- 1.10", "5.0 -- 15.0", "0.98 -- 1.03", "$\\pm$0.05", "0.90 -- 1.10"
  )
)

# Color palette
pal <- list(
  pass         = "A8DDB5",
  fail         = "FDBB84",
  model        = "#A569BD",
  desk_review  = "#2C2C2C",
  ratio_na     = "EEEEEE",
  ratio_colors = c("4575B4", "74ADD1", "66BD63", "FC8D59", "D73027"),
  ratio_values = c(0.70, 0.8999, 0.9001, 1.0999, 1.1001, 1.30),
  ratio_limits = c(0.70, 1.30),
  ratio_breaks = c(0.80, 0.90, 1.00, 1.10, 1.20),
  iaao_band    = "#A8DDB5"
)

iaao_check <- function(metric, value) {
  m <- metric_meta[metric_meta$name == metric, ]
  if (nrow(m) == 0) {
    return(NA)
  }
  value >= m$lo & value <= m$hi
}

iaao_color_cell <- function(metric, value) {
  m <- metric_meta[metric_meta$name == metric, ]
  digits <- if (nrow(m) > 0) m$digits else 4
  v <- round(value, digits)
  passes <- iaao_check(metric, value)
  if (is.na(passes)) {
    return(as.character(v))
  }
  hex <- if (passes) pal$pass else pal$fail
  paste0("\\cellcolor[HTML]{", hex, "} ", v)
}

ratio_to_hex <- function(ratio) {
  rc <- pal$ratio_colors
  case_when(
    is.na(ratio) ~ pal$ratio_na,
    ratio < 0.80 ~ rc[1],
    ratio < 0.90 ~ rc[2],
    ratio <= 1.10 ~ rc[3],
    ratio <= 1.20 ~ rc[4],
    TRUE ~ rc[5]
  )
}

color_ratio_cell <- function(ratio, digits = 3) {
  v <- round(ratio, digits)
  hex <- ratio_to_hex(ratio)
  paste0("\\cellcolor[HTML]{", hex, "} ", v)
}

ratio_fill_scale <- function(name = "Median\nRatio") {
  rc <- paste0("#", pal$ratio_colors)
  scale_fill_gradientn(
    colors   = c(rc[1], rc[2], rc[3], rc[3], rc[4], rc[5]),
    values   = scales::rescale(pal$ratio_values),
    limits   = pal$ratio_limits,
    oob      = scales::squish,
    na.value = paste0("#", pal$ratio_na),
    breaks   = pal$ratio_breaks,
    labels   = sprintf("%.2f", pal$ratio_breaks),
    name     = name
  )
}

caps <- list(
  fig1 = glue(
    "Town-Level IAAO Statistics.",
    "\\newline Green shading meets IAAO standard; orange shading does not."
  ),
  fig2 = glue(
    "IAAO Metrics: Model vs. Desk Review.",
    "\\newline Green shaded band shows the IAAO acceptable range",
    " for each metric."
  ),
  fig3 = glue(
    "Fair Market Values by Group.",
    "\\newline Model and desk review fair market values for properties",
    " with qualifying arm's-length sales (Sold), properties without",
    " a recorded sale (Unsold), and all residential parcels (All).",
    " Sold and Unsold do not sum to All because properties removed",
    " by desk review as outliers are counted in All but neither in",
    " Sold nor Unsold."
  ),
  fig4 = glue(
    "Desk Review Changes by Group.",
    "\\newline Number and share of properties whose value was",
    " changed by desk review."
  ),
  fig5 = glue(
    "Sale Price Ratio Curve.",
    "\\newline Each labeled point is the median ratio within that",
    " sale price decile.",
    " Dotted lines show the IAAO acceptable range (0.9–1.1)."
  ),
  fig6 = glue("Ratio Curve by Sale Price Decile"),
  fig7 = glue(
    "Neighborhood Median Assessment Ratios.",
    "\\newline Green (0.90–1.10) meets the IAAO standard;",
    " Blue indicates under-assessment;",
    " Red indicates over-assessment."
  ),
  fig8 = glue(
    "Neighborhood-Level Median Ratios.",
    "\\newline Blue indicates under-assessment;",
    " Green (0.90–1.1) indicates within standard;",
    " Red indicates over-assessment."
  )
)
```

This is a ratio analysis for **`r town_name` Township** for the `r year_val`
assessment cycle. The initial sale sample had 
**`r format(n_original_sales, big.mark = ",")`** sales: this excludes statistical outliers flagged by the Data department, and had transaction dates ranging from `r min_sale_date` to `r max_sale_date`.  From these,
**`r format(n_excluded_sales, big.mark = ",")`** additional sales were excluded
as outliers by Valuations analysts, leaving a **final sample of
`r format(n_final_sales, big.mark = ",")` sales**. The township
contains **`r format(n_total_pins, big.mark = ",")` residential parcels**. This universe includes Single and Multifamily parcels (up to 6 units) and excludes condo units. Prices range from `r ts$price_range` and are not time-adjusted.

This analysis compares ratio statistics from two stages: 
(1) **Model** values, which are the output of the model, and 
(2) **Desk Review** values, which reflect manual adjustments by staff.

```{r tbl-1}
#| tbl-cap: !expr 'caps$fig1'
#| tbl-pos: H

display_order <- c("Median Ratio", "PRB", "PRD", "COD", "MKI")
met_fac <- function(x) factor(x, levels = display_order)

iaao_table <- data.frame(
  Metric = display_order,
  `IAAO Standard` = metric_meta$standard_label[
    match(display_order, metric_meta$name)
  ],
  Model = c(
    iaao_color_cell("Median Ratio", ts$model_ratio),
    iaao_color_cell("PRB", ts$model_prb),
    iaao_color_cell("PRD", ts$model_prd),
    iaao_color_cell("COD", ts$model_cod),
    iaao_color_cell("MKI", ts$model_mki)
  ),
  `Desk Review` = c(
    iaao_color_cell("Median Ratio", ts$desk_review_ratio),
    iaao_color_cell("PRB", ts$desk_review_prb),
    iaao_color_cell("PRD", ts$desk_review_prd),
    iaao_color_cell("COD", ts$desk_review_cod),
    iaao_color_cell("MKI", ts$desk_review_mki)
  ),
  check.names = FALSE
)

knitr::kable(
  iaao_table,
  format    = "latex",
  escape    = FALSE,
  booktabs  = FALSE,
  linesep   = "",
  col.names = c("Metric", "IAAO Standard", "Model", "Desk Review"),
  align     = c("l", "c", "r", "r")
)
```

```{r fig-2}
#| fig-cap: !expr 'caps$fig2'
#| fig-pos: H
#| fig-cap-location: top
#| fig-height: 3.5
#| fig-width: 6.5

ts_wide <- tibble(
  Metric = met_fac(display_order),
  Model = c(
    ts$model_ratio, ts$model_prb, ts$model_prd,
    ts$model_cod, ts$model_mki
  ),
  `Desk Review` = c(
    ts$desk_review_ratio, ts$desk_review_prb, ts$desk_review_prd,
    ts$desk_review_cod, ts$desk_review_mki
  )
)

ts_long <- ts_wide %>%
  pivot_longer(
    c(Model, `Desk Review`),
    names_to = "Stage", values_to = "Value"
  ) %>%
  mutate(
    Stage  = factor(Stage, levels = c("Model", "Desk Review")),
    digits = metric_meta$digits[match(Metric, metric_meta$name)],
    label  = round(Value, pmin(digits, 2))
  )

iaao_bands <- select(metric_meta, Metric = name, xmin = lo, xmax = hi) %>%
  mutate(Metric = met_fac(Metric))

iaao_meta <- select(metric_meta, Metric = name, mid, half_span) %>%
  mutate(Metric = met_fac(Metric))

sym_anchors <- ts_long %>%
  left_join(iaao_meta, by = "Metric") %>%
  mutate(dev = abs(Value - mid)) %>%
  group_by(Metric, mid, half_span) %>%
  summarize(
    max_dev      = max(dev, na.rm = TRUE),
    out_of_range = any(dev > half_span, na.rm = TRUE),
    .groups      = "drop"
  ) %>%
  filter(out_of_range) %>%
  mutate(
    half_ax = pmax(half_span, max_dev) * 1.15,
    x_lo    = mid - half_ax,
    x_hi    = mid + half_ax
  ) %>%
  select(Metric, x_lo, x_hi) %>%
  pivot_longer(
    c(x_lo, x_hi),
    names_to = "side", values_to = "x"
  ) %>%
  select(Metric, x)

scale_anchors <- bind_rows(
  sym_anchors,
  tibble(Metric = "COD", x = 0)
) %>%
  mutate(Metric = met_fac(Metric))

ggplot() +
  geom_blank(data = ts_long, aes(x = Value, y = 1)) +
  geom_point(
    data  = scale_anchors,
    aes(x = x, y = 1),
    size  = 0,
    alpha = 0
  ) +
  geom_rect(
    data = iaao_bands,
    aes(xmin = xmin, xmax = xmax, ymin = 0.1, ymax = 1.9),
    fill = pal$iaao_band, alpha = 0.45
  ) +
  geom_segment(
    data = ts_wide,
    aes(x = Model, xend = `Desk Review`, y = 1, yend = 1),
    color = "gray40", linewidth = 2, lineend = "round"
  ) +
  geom_point(
    data  = ts_long,
    aes(x = Value, y = 1, color = Stage, shape = Stage),
    size  = 5
  ) +
  geom_text(
    data = ts_long,
    aes(x = Value, y = 1, label = label, color = Stage),
    vjust = -1.6, size = 3, fontface = "bold"
  ) +
  facet_wrap(~Metric, scales = "free_x", ncol = 1, strip.position = "left") +
  scale_color_manual(
    values = c("Model" = pal$model, "Desk Review" = pal$desk_review)
  ) +
  scale_shape_manual(values = c("Model" = 16, "Desk Review" = 17)) +
  scale_y_continuous(limits = c(0, 2)) +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.text.y.left = element_text(
      face = "bold", size = 11, angle = 0, hjust = 1
    ),
    strip.placement = "outside",
    legend.position = "bottom",
    plot.margin = margin(t = 20, r = 5, b = 5, l = 5, unit = "pt")
  ) +
  labs(x = NULL, y = NULL, color = "Stage", shape = "Stage")
```

```{r desc-helpers}
no_sale <- all_parcels %>% filter(is.na(sale_price))

fmt_n <- function(x) format(x, big.mark = ",")
fmt_dol <- function(x) paste0("\\$", format(round(x), big.mark = ","))
fmt_pct <- function(changed, total) {
  paste0(round(changed / total * 100, 1), "\\%")
}
n_changed <- function(df) {
  sum(!is.na(df$model_FMV) & !is.na(df$desk_review_FMV) &
    df$model_FMV != df$desk_review_FMV) # nolint: indentation_linter.
}
```

{{< pagebreak >}}

```{r tbl-3}
#| tbl-cap: !expr 'caps$fig3'
#| tbl-pos: H

groups <- list(Sold = sales_df, Unsold = no_sale, All = all_parcels)

mv_table <- tibble(
  Group = names(groups),
  `Median Model FMV` = sapply(
    groups, \(d) fmt_dol(median(d$model_FMV, na.rm = TRUE))
  ),
  `Median DR FMV` = sapply(
    groups, \(d) fmt_dol(median(d$desk_review_FMV, na.rm = TRUE))
  ),
  `Mean Model FMV` = sapply(
    groups, \(d) fmt_dol(mean(d$model_FMV, na.rm = TRUE))
  ),
  `Mean DR FMV` = sapply(
    groups, \(d) fmt_dol(mean(d$desk_review_FMV, na.rm = TRUE))
  )
)

knitr::kable(
  mv_table,
  format   = "latex",
  escape   = FALSE,
  booktabs = FALSE,
  linesep  = "",
  align    = c("l", "r", "r", "r", "r")
)
```

```{r tbl-4}
#| tbl-cap: !expr 'caps$fig4'
#| tbl-pos: H

changes_table <- tibble(
  Group = c("Sold", "Unsold", "All"),
  N = c(
    fmt_n(nrow(sales_df)),
    fmt_n(nrow(no_sale)),
    fmt_n(nrow(all_parcels))
  ),
  `N DR Changes` = c(
    fmt_n(n_changed(sales_df)),
    fmt_n(n_changed(no_sale)),
    fmt_n(n_changed(all_parcels))
  ),
  `\\% DR Changes` = c(
    fmt_pct(n_changed(sales_df), nrow(sales_df)),
    fmt_pct(n_changed(no_sale), nrow(no_sale)),
    fmt_pct(n_changed(all_parcels), nrow(all_parcels))
  )
)

knitr::kable(
  changes_table,
  format   = "latex",
  escape   = FALSE,
  booktabs = FALSE,
  linesep  = "",
  align    = c("l", "r", "r", "r")
)
```

```{r nbhd-ratios-prep}
nbhd_ratios <- all_parcels %>%
  filter(!is.na(sale_price), !sale_excluded %in% TRUE) %>%
  mutate(neighborhood_number = gsub("-", "", neighborhood_number)) %>%
  summarize(
    model_ratio = median(model_sale_ratio, na.rm = TRUE),
    dr_ratio    = median(desk_review_sale_ratio, na.rm = TRUE),
    n_sales     = n(),
    .by         = neighborhood_number
  )
```

{{< pagebreak >}}

```{r fig-5}
#| fig-cap: !expr 'caps$fig5'
#| fig-pos: H
#| fig-cap-location: top
#| fig-height: 3.5
#| fig-width: 7

decile_long <- decile_stats %>%
  select(price_decile, model_ratio, desk_review_ratio) %>%
  pivot_longer(
    cols      = c(model_ratio, desk_review_ratio),
    names_to  = "Stage",
    values_to = "Sale Ratio"
  ) %>%
  mutate(
    Stage = case_when(
      Stage == "model_ratio" ~ "Model",
      Stage == "desk_review_ratio" ~ "Desk Review"
    ),
    Stage = factor(Stage, levels = c("Model", "Desk Review"))
  )

axis_labels <- all_parcels %>%
  filter(!is.na(sale_price), !sale_excluded %in% TRUE, !is.na(price_decile)) %>%
  summarize(
    min_price = min(sale_price),
    max_price = max(sale_price),
    .by       = price_decile
  ) %>%
  arrange(price_decile) %>%
  mutate(label = paste0(
    price_decile, "\n",
    scales::dollar(min_price, scale_cut = scales::cut_short_scale()),
    "–\n",
    scales::dollar(max_price, scale_cut = scales::cut_short_scale())
  )) %>%
  (\(df) setNames(df$label, df$price_decile))()

y_min <- min(decile_long$`Sale Ratio`, 0.7, na.rm = TRUE)
y_max <- max(decile_long$`Sale Ratio`, 1.3, na.rm = TRUE)

ggplot(
  decile_long,
  aes(
    x     = price_decile,
    y     = `Sale Ratio`,
    group = Stage,
    color = Stage,
    label = round(`Sale Ratio`, 2)
  )
) +
  annotate("rect",
    xmin = -Inf, xmax = Inf, ymin = 0.9, ymax = 1.1,
    fill = pal$iaao_band, alpha = 0.12
  ) +
  geom_hline(yintercept = 1, color = "darkgreen", linewidth = 1) +
  geom_hline(
    yintercept = 0.9, linetype = "dotted", color = "black", linewidth = 0.8
  ) +
  geom_hline(
    yintercept = 1.1, linetype = "dotted", color = "black", linewidth = 0.8
  ) +
  annotate("text",
    x = 1, y = 1.11,
    label = "IAAO Range (0.9–1.1)", hjust = 0, vjust = -0.4, size = 3.5
  ) +
  geom_line(linewidth = 1) +
  geom_label(show.legend = FALSE, size = 3) +
  scale_color_manual(
    values = c("Model" = pal$model, "Desk Review" = pal$desk_review)
  ) +
  scale_x_continuous(breaks = 1:10, labels = axis_labels) +
  scale_y_continuous(
    breaks = seq(floor(y_min * 10) / 10, ceiling(y_max * 10) / 10, by = 0.1)
  ) +
  coord_cartesian(ylim = c(y_min, y_max)) +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(size = 7.5)) +
  labs(x = "Sale Price Decile", y = "Median Sale Ratio", color = "Stage")
```

```{r tbl-6}
#| tbl-cap: !expr 'caps$fig6'
#| tbl-pos: H
#| tbl-cap-location: top

decile_display <- decile_stats %>%
  select(
    Decile        = price_decile,
    `Price Range` = price_range,
    `N Sales`     = number_of_sales,
    `Model Ratio` = model_ratio,
    `DR Ratio`    = desk_review_ratio
  ) %>%
  mutate(
    `Model Ratio` = round(`Model Ratio`, 3),
    `DR Ratio`    = round(`DR Ratio`, 3)
  )

knitr::kable(
  decile_display,
  format   = "latex",
  booktabs = TRUE,
  linesep  = "",
  align    = c("c", "l", "r", "r", "r")
)
```

```{r fig-7-prep}
neighborhoods <- ccao::nbhd_shp %>%
  filter(township_name == town_name) %>%
  select(town_nbhd, geometry)

map_data <- neighborhoods %>%
  left_join(nbhd_ratios, by = c("town_nbhd" = "neighborhood_number"))

map_theme <- theme_void(base_size = 9) +
  theme(
    legend.position = "right",
    plot.title      = element_text(face = "bold", size = 10)
  )

make_map <- function(col, title) {
  ggplot() +
    annotation_map_tile(type = "cartolight", zoomin = 0) +
    geom_sf(
      data = map_data, aes(fill = .data[[col]]), alpha = 0.85, linewidth = 0.1
    ) +
    ratio_fill_scale() +
    map_theme +
    labs(title = title)
}

map_model <- make_map("model_ratio", "Model")
map_dr <- make_map("dr_ratio", "Desk Review")
```

```{r fig-7}
#| fig-cap: !expr 'caps$fig7'
#| fig-pos: H
#| fig-cap-location: top
#| fig-height: 3.5
#| fig-width: 8.5
#| results: 'hide'

grid.newpage()
print(map_model, vp = viewport(
  x = 0, y = 0, width = 1 / 2, height = 1,
  just = c("left", "bottom")
))
print(map_dr, vp = viewport(
  x = 1 / 2, y = 0, width = 1 / 2, height = 1,
  just = c("left", "bottom")
))
```


```{r tbl-8}
#| tbl-cap: !expr 'caps$fig8'
#| tbl-cap-location: top
#| tbl-pos: H

all_nbhds <- all_parcels %>%
  distinct(neighborhood_number) %>%
  arrange(neighborhood_number)

nbhd_table_data <- all_nbhds %>%
  left_join(nbhd_ratios, by = "neighborhood_number") %>%
  mutate(
    `NBHD` = neighborhood_number,
    `Model Ratio` = ifelse(
      is.na(model_ratio), "---", color_ratio_cell(model_ratio, digits = 3)
    ),
    `DR Ratio` = ifelse(
      is.na(dr_ratio), "---", color_ratio_cell(dr_ratio, digits = 3)
    ),
    `N Sales` = as.character(ifelse(is.na(n_sales), 0L, n_sales))
  ) %>%
  select(`NBHD`, `Model Ratio`, `DR Ratio`, `N Sales`)

n <- nrow(nbhd_table_data)
half <- ceiling(n / 2)
pad <- half - (n - half)

right_half <- bind_rows(
  nbhd_table_data[(half + 1):n, ],
  if (pad > 0) {
    tibble(
      NBHD = rep("", pad), `Model Ratio` = rep("", pad),
      `DR Ratio` = rep("", pad), `N Sales` = rep("", pad)
    )
  }
)

spacer <- tibble(` ` = rep("", half))

knitr::kable(
  cbind(nbhd_table_data[1:half, ], spacer, right_half),
  format = "latex",
  escape = FALSE,
  booktabs = FALSE,
  linesep = "",
  align = c("l", "r", "r", "r", "l", "l", "r", "r", "r"),
  col.names = c(
    "NBHD", "Model Ratio", "DR Ratio", "N Sales", "",
    "NBHD", "Model Ratio", "DR Ratio", "N Sales"
  )
)
```
